The \dealii Library, Version 9.5

### 2023-06-22 9.5/paper.tex
minor

solver.residual            = [&](const VectorType &x,
                                 VectorType       &F) {/*...*/};
solver.setup_jacobian      = [&](const VectorType &x) {/*...*/};
solver.solve_with_jacobian = [&](const VectorType &rhs,
                                 VectorType       &sol) {/*...*/};
solver.solve(x);
\end{c++}
The default configuration is set up to use a Jacobian-free Newton-Krylov (JFNK)
approach~\cite{knoll2004jacobian}, using \texttt{solve\_with\_jacobian} as linear solver.
Numerous other solver configurations are possible and can be selected
programmatically, or via the powerful command line customization of \petsc.
This includes for example Quasi-Newton methods, Anderson's acceleration, and
nonlinear preconditioning~\cite{brune2015composing}.

@@

// If solving udot = G(t,u)
solver.explicit_function = [&](const double     t,
                               const VectorType &u,
                               VectorType       &G) {/*...*/};
// If solving F(t,u,udot) = 0
solver.implicit_function = [&](const double     t,
                               const VectorType &u,
                               const VectorType &udot,
                               VectorType       &F) {/*...*/};
\end{c++}
In addition to specifying the function callbacks, users can further customize
the solution of the linearized equations $\alpha * \frac{\partial{F}}{\partial{\dot{u}}} + \frac{\partial{F}}{\partial{u}}$
via the callbacks:
\begin{c++}
solver.setup_jacobian = [&](const double     t,
                            const VectorType &u,
                            const VectorType &udot,
                            const double     alpha) {/*...*/};
solver.solve_with_jacobian = [&](const VectorType &rhs,
                                 VectorType       &sol) {/*...*/};
\end{c++}
As for \snes, the default configuration of an implicit solver is set up to
a JFNK approach, and the entire suite of solvers offered by PETSc is available,
including adaptive time-stepping and Implicit-Explicit schemes.

@@

We refer interested readers to our documentation for other more advanced
functions of the \snes, \ts and \petscsf wrappers, and to the {\tt tests/petsc/} folder
for examples on how to use them.

>>>>

solver.residual            = [&](const VectorType &x,
                                 VectorType       &F) {/*...*/};
solver.setup_jacobian      = [&](const VectorType &x) {/*...*/};
solver.solve_with_jacobian = [&](const VectorType &rhs,
                                 VectorType       &sol) {/*...*/};
solver.solve(x);
\end{c++}
The default configuration is set up to use a Jacobian-free Newton-Krylov (JFNK)
approach~\cite{knoll2004jacobian}, using \texttt{solve\_with\_jacobian} as linear solver.
Numerous other solver configurations are possible and can be selected
programmatically using the constructor arguments,
or via the powerful command line customization of \petsc.
This includes for example Quasi-Newton methods, Anderson's acceleration, and
nonlinear preconditioning~\cite{brune2015composing}.

@@

// If solving udot = G(t,u)
solver.explicit_function = [&](const double     t,
                               const VectorType &u,
                               VectorType       &G) {/*...*/};
// If solving F(t,u,udot) = 0
solver.implicit_function = [&](const double     t,
                               const VectorType &u,
                               const VectorType &udot,
                               VectorType       &F) {/*...*/};
\end{c++}
In addition to specifying the function callbacks, users can further customize
the solution of the linearized equations $\alpha * \frac{\partial{F}}{\partial{\dot{u}}} + \frac{\partial{F}}{\partial{u}}$
via the callbacks:
\begin{c++}
solver.setup_jacobian = [&](const double     t,
                            const VectorType &u,
                            const VectorType &udot,
                            const double     alpha) {/*...*/};
solver.solve_with_jacobian = [&](const VectorType &rhs,
                                 VectorType       &sol) {/*...*/};
\end{c++}
As for \snes, the default configuration of an implicit solver is set up to
use a JFNK approach, and the entire suite of solvers offered by PETSc is available
programmatically or via the command line interface,
including adaptive time-stepping and Implicit-Explicit schemes.

@@

We refer interested readers to our documentation for more advanced
functions of the \snes, \ts and \petscsf wrappers, and to the {\tt tests/petsc/} folder
for examples on how to use them.
